%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{article} % Default font size and paper size
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\usepackage[hyphens]{url}
\usepackage{xunicode,xltxtra,parskip} % Formatting packages
\usepackage[official]{eurosym}
\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors
\usepackage[paper=a4paper, % Change to letterpaper for US letter
	inner=1cm, % Inner margin
	outer=1.5cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm]{geometry} % Outer margin]{geometry}
%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}

% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{bbding}
\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{6pt}{6pt} % Spacing around sections

\begin{document}

\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\par{{\Large Ingmar René \textsc{Staude}  -- Curriculum Vitae}\bigskip\par} % Your name
\begin{tabular}{rl}
\textsc{Address:} & Brockhausstr. 47, 04229 Leipzig\\
\textsc{Email:} & \href{mailto:staudeingmar@gmail.com}{staudeingmar@gmail.com}\\

\textsc{Homepage:} & \href{istaude@github.io}{istaude@github.io}\
\end{tabular}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}


\textbf{German Centre for Integrative Biodiversity Research}  \hfill Germany\\
\textit{DPhil in \textsc{Biodiversity Conservation} \hfill 2017 - ongoing}\\
\small Advisor: Henrique Pereira\normalsize\ \\

 \textbf{Université de Poitiers} \hfill France \\
\textbf{Universidade de Coimbra} \hfill Portugal\\
\textbf{Universidade Federal do Rio Grande do Sul} \hfill Brazil\\
\textit{International Master of Science in \textsc{Applied Ecology} \hfill 2015 - 2017}\\
\small Advisor: Gerhard Overbeck \\
\textit{magna cum laude; \textsc{Gpa}: 4.8/5}\normalsize \\

\textbf{Universidad San Francisco de Quito} \hfill Ecuador \\
\textit{Fieldwork and research \hfill Jan - Mar 2016}  \\
\small{in the Northern Andean páramo, Amazon rainforest and Galapagos islands}\normalsize  \\


\textbf{Freie Universität Berlin} \hfill Germany\\
\textit{Bachelor of Science in \textsc{Biology} \hfill 2011 - 2015}\\
\small Advisor: Thomas Schmülling\\
\textit{magna cum laude; \textsc{Gpa}: 1.3/1} \normalsize \\

\textbf{University Centre in Svalbard} \hfill Spitzbergen \\ 
\textit{Fieldwork and research \hfill Jul - Dec 2014} \\
\small{in the Greenland Sea, Arctic Ocean, Tundra and Polar Desert}\normalsize \\

\section{Professional Experience}


\textbf{Humbolt Universität zu Berlin} \hfill Germany\\
\textit{Behavioural Ecology \hfill Mar - Aug 2015}\\
\small{Research assistant | Advisor: Bernd Ronacher}\normalsize  \\ 

\textbf{Charité - Universitätsmedizin Berlin} \hfill Germany\\
\textit{Neuroimaging \hfill Feb--Jul 2014} \\
\small{Research experience as undergraduate | Advisor: Chantal Mörsen}\normalsize \\ 


\textbf{Freie Universität Berlin} \hfill Germany\\
\textit{Applied plant genetics \hfill Nov 2013 - Mar 2014} \\
\small{Research assistant | Advisor: Thomas Schmülling}\normalsize  \\ 

\textbf{LMW2 Partners \& Normandy Real Estate} \hfill New York, USA\\
\textit{Venture capital and real estate investment \hfill Jul - Sep 2013} \\
\small{Summer intern | Advisor: Finn Wentworth}\normalsize \\ 


\section{Teaching Experiences: Courses TA'd}

\normalsize\textbf{Nature Conservation} for master students \hfill Portugal\\
Organized fieldwork and supervised student projects in Peneda-Gerês National Park \textit{\hfill 2018, 2019} \\
\small\textit{Martin-Luther-Universität Halle-Wittenberg} \\

\normalsize\textbf{Spatial Ecology and Modelling} for master students \hfill Germany\\
Ran coding tutorials \textit{\hfill 2018, 2019}\\
\small\textit{Martin-Luther-Universität Halle-Wittenberg} \\

\normalsize\textbf{iDiv Summer School: Ecological Theory and Modelling for the Biodiversity Crisis}\hfill Germany \\
Ran coding tutorials \textit{\hfill 2018}\\
\small\textit{German Centre for Integrative Biodiversity Research} \\

\normalsize\textbf{Urban Vegetation} for master students \hfill Brazil\\
Ran lecture on nexus of urban infrastructure and biodiversity \textit{\hfill 2017}\\
Invited by students as plenary speaker at the "Academic Week of Biology UFRGS 2017"\\
\small\textit{Universidade Federal de Rio Grande do Sul} \\


\section{Academic mentoring}
\normalsize\textbf{Master students (as supervisor)}: iDiv\\
\normalsize\textbf{2021--ongoing:} How threatened are plants in Europe? A national Red List synthesis (\textit{H. Holz})



\section{Publications}

\normalsize\textbf{Ingmar R. Staude}, Henrique M. Pereira, \ldots\ \& Lander Baeten. Consistent replacement of small- by large-ranged plant species across habitats. \textit{Submitted (2021).} Pre-print available at https://ecoevorxiv.org/ujky2/ \\

\textbf{Ingmar R. Staude}, Gerhard E. Overbeck, \ldots\ \& Henrique M. Pereira. Generalist birds make room for specialists in grassland remnants as land use change intensifies. \textit{Frontiers in Ecolgy and Evolution} (2021). 8:597542.\\

\textbf{Ingmar R. Staude}, Donald M. Waller, \ldots\ \& Lander Baeten. Replacements of small- by large-ranged species scale up to diversity loss in Europe's temperate forest biome. \textit{Nature Ecology \& Evolution} (2020). 4:802–808.\\

\textbf{Ingmar R. Staude}, Laetitia M. Navarro \& Henrique M. Pereira. Range size predicts the risk of local extinction from habitat loss. \textit{Global Ecology and Biogeography} (2020). 29.1:16-25.\\

\textbf{Ingmar R. Staude}, Eduardo Vélez-Martin, \ldots\ \& Gerhard E. Overbeck. Local biodiversity erosion in south Brazilian grasslands under moderate levels of landscape habitat loss. \textit{Journal of Applied Ecology} (2018). 55.3:1241-1251.\\


\section{Media Coverage}
\textbf{Press Release:} "Plant diversity in European forests is declining", featured in e.g. Spektrum, Deutschlandfunk Nova, Phys.org and Science Bulletin \href{https://www.nature.com/articles/s41559-020-1176-8/metrics}{\textit{link}}\\
\textbf{Press Release:} "Biodiversity erosion in Brazil due to land use change: the case of grasslands",
Journal of Applied Ecology Blog, \href{https://appliedecologistsblog.com/2018/01/31/biodiversity-erosion-in-brazil-due-to-land-use-change-the-case-of-grasslands/}{\textit{link}}\\

\section{Working Groups}
\normalsize\textbf{Synthesis Centre on Biodiversity and Ecosystem Services} \hfill Brazil \\
\textit{GrassSyn \hfill 2020}\\
\small{Biodiversity of Brazilian grasslands and savannas: patterns and
drivers, ecosystem services, and strategies for conservation and restoration; Participant}\normalsize \\

\normalsize\textbf{German Centre for Integrative Biodiversity Research} \hfill Germany\\
\textit{sReplot} \hfill \textit{2018, 2019}\\
\small{ Upscaling of individual species dynamics to community trends in biodiversity and composition using vegetation change data sets; Participant}\\


\section{Professional Skills}
\begin{tabular}{ll}
Software & R, {\fb \LaTeX}, Markdown, Git, Stan\\
Languages & English, Portuguese (excellent); French (intermediate); German (native) 
\end{tabular}\\

\section{Peer reviews for journals}
\textit{Frontiers in Biogeography, Ecography}

%----------------------------------------------------------------------------------------
%	INTERESTS AND ACTIVITIES
%----------------------------------------------------------------------------------------
\section{References}
Prof. Dr.\textbf{ Henrique Pereira}, iDiv \Phone +49 341 9733137. \href{mailto:hpereira@idiv.de}{hpereira@idiv.de} \\
Prof. Dr. \textbf{Gerhard E. Overbeck}, UFRGS \Phone +55 51 3308 7557. \href{mailto:gerhard.overbeck@ufrgs.br}{gerhard.overbeck@ufrgs.br}\\[1cm]\\


%----------------------------------------------------------------------------------------

\end{document}
